Collocated Snapshot Backup with VM-Centric Deduplication in the Cloud

### 2013-09-26 snapshot_system/fast14_introduction.tex
revise

The paper studies and evaluates  an integrated approach which uses  multiple duplicate detection strategies
based on  version  detection, similarity guided local deduplication,
and popularity guided global deduplication. 
This approach is VM centric by localizing duplicate detection within each VM  
and by packaging only data chunks from the same VM into a file system block as much as possible.
By narrowing duplicate sharing within a small percent of common data chunks and exploiting their popularity,
this scheme can afford to allocate extra replicas of these shared chunks for better
fault resilience while sustaining competitive deduplication efficiency.
Localization also brings the benefits of greater ability to exploit parallelism so
backup operations can run simultaneously without a central  bottleneck.
This  VM-centric solution uses  a small amount of  memory while delivering a reasonable deduplication efficiency.

@@

%************** Paper sections summary
%THIS NEEDS MODIFICATION
The rest of this paper is organized as follows.
Section~\ref{sect:background} reviews the background and discusses the  design options for snapshot backup 
with a VM-centric approach. 
Section~\ref{sect:deduplication}  analyzes the tradeoffs and benefits of our approach. 
Section~\ref{sect:architecture}  describes our system architecture and implementation details.
%   the benefit of our approach for fault isolation. 
Section~\ref{sect:evaluation} is our experimental evaluation that compares with other approaches.
Section~\ref{sect:conclusion}  concludes this paper.

>>>>

The paper studies and evaluates  an integrated approach which uses  multiple duplicate detection strategies
based on  version  detection, similarity guided local deduplication,
and popularity guided global deduplication. 
This approach is VM centric by localizing duplicate detection within each VM  
and by packaging only data chunks from the same VM into a file system block as much as possible.
By narrowing duplicate sharing within a small percent of common data chunks and exploiting their popularity,
this scheme can afford to allocate extra replicas of these shared chunks for better
fault resilience while sustaining competitive deduplication efficiency.
Localization also brings the benefits of greater ability to exploit parallelism so
backup operations can run simultaneously without a central  bottleneck.
This  VM-centric solution uses  a small amount of  memory while delivering reasonable deduplication efficiency.

@@

%************** Paper sections summary
%THIS NEEDS MODIFICATION
The rest of this paper is organized as follows.
Section~\ref{sect:background} reviews the background and discusses the  design options for snapshot backup 
with a VM-centric approach. 
Section~\ref{sect:deduplication}  analyzes the tradeoff and benefits of our approach. 
Section~\ref{sect:architecture}  describes our system architecture and implementation details.
%   the benefit of our approach for fault isolation. 
Section~\ref{sect:evaluation} is our experimental evaluation that compares with other approaches.
Section~\ref{sect:conclusion}  concludes this paper.
